Trends of SDR in Thessaloniki

### 2023-08-31 Article.Rmd
Commit 2023-08-31 20:14

<!-- \footnotesize -->
```{r trendseasontable, echo=F}
pp <- read.csv("./figures/tbl_longterm_trends_season.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE)
pp <- pp[grep("SDR" ,pp$var), ]
pp$slope.sd           <- NULL
pp$slope.ConfInt_0.95 <- NULL
pp$slope.ConfInt_0.99 <- NULL
pp$var                <- NULL
rownames(pp)          <- NULL
names(pp) <- c("Trend [%/year]", "Trend p-value", "Sky condition", "Season", "Trend statistical signif. [%]")
## order by season
target    <- c("Winter", "Spring", "Summer", "Autumn")
new_order <- sapply(target, function(x,pp){which(pp$Season == x)}, pp=pp)
pp        <- pp[new_order,]
## numeric precision
pp$`Trend [%/year]` <- signif(pp$`Trend [%/year]`, 3)
pp$`Trend p-value`  <- signif(pp$`Trend p-value`,  3)

>>>>

<!-- \footnotesize -->
```{r trendseasontable, echo=F}
pp <- read.csv("./figures/tbl_longterm_trends_season.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE)
pp <- pp[grep("SDR" ,pp$var), ]
pp$slope.sd           <- NULL
pp$slope.ConfInt_0.95 <- NULL
pp$slope.ConfInt_0.99 <- NULL
pp$var                <- NULL
rownames(pp)          <- NULL
names(pp) <- c("Trend [%/year]", "Trend p-value", "Sky condition", "Season", "Statistical signif. [%]")
## order by season
target    <- c("Winter", "Spring", "Summer", "Autumn")
new_order <- sapply(target, function(x,pp){which(pp$Season == x)}, pp=pp)
pp        <- pp[new_order,]
## numeric precision
pp$`Trend [%/year]`          <- signif(pp$`Trend [%/year]`, 3)
pp$`Trend p-value`           <- signif(pp$`Trend p-value`,  3)
pp$`Statistical signif. [%]` <- signif(pp$`Statistical signif. [%]`,  3)
